Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}

### 2025-02-13 paper_jar/paper.tex
Revise

Both of our AL approaches outperform random sampling.
However, the performance differences are not significant for a Wilcoxon signed-rank test with $\alpha = 0.05$ and also depend on the fraction of the runtime sampled (cf.~Fig.~\ref{fig:annitraincolorselection}).
However, a clear advantage of our approach is that it indicates when to stop adding new instances.
While the active learning results on the full dataset are not as strong as on the smaller tuning dataset, they still show the benefit of making the benchmark selection dependent on the solvers to be distinguished.

>>>>

Both of our AL approaches outperform random sampling.
However, the performance differences are not significant for a Wilcoxon signed-rank test with $\alpha = 0.05$ and also depend on the fraction of the runtime sampled (cf.~Fig.~\ref{fig:annitraincolorselection}).
\change{However, an advantage of our approach is that it indicates when to stop adding new instances.
Recall that Figure~\ref{fig:annitrainoptgoalacc} shows the trade-offs of the amount of sampled instances and the ranking accuracy.
Active-learning helps to identify the optimal region as sampling too many instances only provides marginal improvements compared to its cost.}
